Mutual Coherence Minimization \\via Projection Matrices\\ for CSM EENG 515

### 2018-12-11 paper.tex
Update paper.tex

\section{Introduction}
\IEEEPARstart{T}{he} reduction of Mutual Coherence of sensing systems has long plagued
those who need to measure quantities. It is important that if multiple measurements
are taken, that there is not too much redundant information about the underlying 
process being measured. Through Compressive Sensing (CS) techniques, it is possible to achieve
a smaller amount of required measurements. Typically, these techniques involve a sparse
sampling of an over-complete dictionary which could describe the signal being sampled. This 
motivates the question: What is the "best" sparse sampling? \\
This paper examines one method in particular for determining optimal sparse signal 
dictionaries and sampling matrices. First mutual coherence minimization is explored

@@

must be made to the problem to provide a solution other that brute force checking of every possible

@@

@@

It should be noted that this is not the greatest upper bound of MC, and that it is not always
achieved. This will be demonstrated in the higher dimensional examples. \\
There have been different techniques used to minimize MC recently, some of which include: the algorithm of Elad [Elad's paper], the algorithm of Duarte-Carajalino and Sapiro [DC and S paper], the algorithm of Xu et al [Xu's paper], and the algorithm of Obermeier and Martinez-Lorenzo [Obermeeir's paper]. 

@@

\includegraphics[width=2.8in]{comparison.png}
\caption{Plots of the averaged mutual coherence of a matrix of size $m \times n$ v.s. number of rows $m$.}

@@

$\ldots$ \\
Another important technique used is the projection onto the $l_1$ ball $\ldots$\\
Proximal Gradient Techniques: $\ldots$

@@

\subsection{Projection onto $l_1$ ball}

@@

The method of Lin et al. for direct mutual coherence minimization involves estimating the gradient of the dictionary
($\Delta D$) through a projection onto the $l_1$ ball. A factor $V$ must be calculated which is

@@

After this factor $V$ has been found:

@@

    \Delta D = M(V + V^T)

@@

And to iterate for new columns of D:
This method represents the proximal gradient method for mutual coherence minimization.

@@

@@

@@

@@

\caption{The MC falls quiclkly in the first iteration before oscilating wildly on its way towards a

@@

\bigskip \\

@@

where $\|A \|_{\infty}=\max\limits_{i,j}(a_{ij})$ means the $\ell_{\infty}$-norm of a matrix $A$. We substract the identity matrix to avoid the influence of diagonal elements, because according to the mutual coherence definition we are interested in angle between the different columns $i\neq j$. \\

@@

In order to solve this problem we used the algorith proposed in [refer ball].

$\hdots$\\
To achieve mutual coherence minimization, a smoothed gradient descent technique is used.
First it is applied to the overall sensing matrix $M$. \\
$\hdots$\\
The lower bound for mutual coherence for any $m\times n$ matrix is given as:
\begin{equation}
\mu(M) \geq \sqrt{\frac{n - m}{m(n-1}}
\end{equation}
\subsection{Minimizing Total Mutual Coherence}

\section{Results}
\subsection{Mutual Coherence Minimization}
Consider $D \in \mathbb{R}^{m\times n}$:
\begin{align}
    D = \begin{bmatrix} 0 &1 &\>\>\>\sqrt{2}/2 \\
                        1 &0 &-\sqrt{2}/2 \end{bmatrix}
\end{align}
Then it has MC and Welch bound:
\begin{align}
\mu (D) &= \sqrt{2}/2 \\
\mu_{WB} (D) &= 0.5
\end{align}
After application of Lin's algorithm to the matrix, a new matrix is returned:
\begin{align}
    D = \left[\begin{array}{ccc} 0.966 & -0.258  &0.707\\ -0.259 & 0.966 & 0.707 \end{array}\right] 
\end{align}
And the new MC:
\begin{align}
\mu (M) &= 0.500 \\[1em]
\end{align}
Note that any unitary transformation (rotation) of this matrix will also have the minimum possible MC for
matrices in $\mathbb{R}^{2 \times 3}$.
\subsection{Problems with stability}

\subsection{Improving stability}

\section{Conclusion}
This document has demonstrated how to minimize the mutual coherence of a sampling
matrix via projection. $\ldots$

>>>>

\section{Introduction}
\IEEEPARstart{T}{he} reduction of Mutual Coherence (MC) of sensing systems has long plagued
those who need to measure quantities. It is important that if multiple measurements
are taken, that there is not too much redundant information about the underlying 
process being measured. Through Compressive Sensing (CS) techniques, it is possible to achieve
a smaller amount of required measurements. Typically, these techniques involve a sparse
sampling of an over-complete dictionary which is able to describe the signal being sampled. This 
motivates the question: What is the "best" sparse sampling? \\
This paper examines one method in particular for determining optimal sparse signal 
dictionaries and sampling matrices. First mutual coherence minimization is explored as well
as the relevant mathematics required for its minimization. Then a lower dimensional example
of MC minimization is covered followed by a higher dimensional example involving MC reduction
via a projection matrix. Finally, this method is compared to other current methods.

@@

must be made to the problem to provide a solution other than brute force checking of every possible

@@

Alternativly, this may be written as:
    \mu(M) = ||M^T M - I||_\infty

@@

It should be noted that this is not the greatest lower bound of MC, and that it is not always
achieved. The true lower limit of MC for a particular dictionary depends only on its dimension. This will be demonstrated in the higher dimensional examples. \\
There have been different techniques used to minimize MC recently, some of which include: Elad's algorithm [Elad's paper], the algorithm of Duarte-Carajalino and Sapiro [DC and S paper], the algorithm of Xu et al [Xu's paper], the algorithm of Lin et al., and the algorithm of Obermeier and Martinez-Lorenzo [Obermeeir's paper]. The Fig.~1 shows the comparison between performance of different algorithms as well as mutual coherence of a random matrix build by using the uniform distribution (the random matrices initially have small mutual coherence because their entries independent).  \\

@@

\includegraphics[width=3in]{comparison_for_paper.pdf}
\caption{Plots of the averaged mutual coherence of a matrix of size $m \times n$ v.s. number of rows $m$ with fixed number of columns $n$ (From Lin et al. (ref))}

@@

As you could see from the figure (Fig.~1), the algorithms of Lin et al. has superior performance compared with other algorithms. Also it is worth noting to that the Welch bound is not achieved by any algorithm.  The Fig 1. does not include the algorithm of Obermeier and Martinez-Lorenzo, but as they mention in their paper that the Welch bound is not achieved as well. \\
The algorithms proposed in the paper use the Gram matrix to find the matrix with a low mutual coherence. The Lin's et al. proposes to direct mutual coherence minimization. The algorithm of Obermeier and Martinez-Lorenzo uses the Lagrangian the Augmented Lagrangian method and the columns of the sensing matrix should be computed by a differentiable function. We decided to choose the paper by Lin et al., because this paper contains clear and detailed description of the algorithm as well as the material has a good correlation with material we have learn in the class.

Another important technique used is the projection onto the $\ell_1$ ball. One possible way is to do that by the method proposed by  Duchi et al. This problem could be formulated as
   \min\limits_{\mathbf{w}\in\mathbb{R}^n} \|\mathbf{w}-\mathbf{v} \|^2_2 \quad \mathrm{s.t.} \quad \|\mathbf{w} \|_1 \leq r, 
where $r$ is the radius of the $\ell_1$ ball, $\mathbf{v}\in\mathbb{R}^n$ the vector we would like to project onto the $\ell_1$ ball, and $\mathbf{w}$ is the result of the projection.  \\
%Proximal Gradient Techniques: $\ldots$
This $\ell_1$ projection technique is very useful for accomplishing the next technique.
In the algorithm of Lin et al. a technique is used called the proximal gradient method. This method is
a generalized form of gradient descent which may apply to functions which are not differentiable 
(such as the $\ell_0$ norm). In this method the objective function is able to be smoothed in some way. 
For example, suppose one wishes to maximize an inner product while maintaining an $\ell_1$ norm size 
constraint.
f(M) = \max_{||\mathbf{V}|| \leq 1} <M^T M - I, V>
This $\ell_1$ norm constraint makes this a nondifferentiable expression, however, a smooth approximation
may be made through the addition of a term:
    f_\rho(M) = \max_{||\mathbf{V}|| \leq 1} <M^T M - I, V> - \frac{\rho}{2}||V||_F^2
Where $\rho$ is a smoothing factor. Then the gradient of this smoothed function may be approximated by:
    \Delta f_\rho(M) = M(V + V^T)
Where $V$ is the projection of $(M^T M - I)/\rho$ onto the $\ell_1$ ball.

@@

%\subsection{Projection onto $l_1$ ball}

@@

The method of Lin et al. for direct mutual coherence minimization involves estimating the gradient 
of the objective function of dictionary mutual coherence.
    f(M) = \max_{||\mathbf{V}|| \leq 1} <M^T M - I, V>
($\Delta D$) through a projection onto the $l_1$ ball. At each iteration, a factor $V$ 
must be calculated which is

@@

After this factor $V$ has been found, the gradient approximation for the current iteration is given as:

@@

    \Delta D_k = M_k(V + V^T)

@@

And to iterate for new columns of D, the equation of iteration is:

@@

\label{eq:iterate}

@@

This method of first computing $V$ (which yields $\Delta D$) and then iterating $D$ using
Equation~\ref{eq:iterate} represents the proximal gradient method for MC minimization.

@@

It should be seen that in this case in $\mathbb{R}^{2\times3}$ the Welch bound for MC of 0.5 is 
actually achieved. This is not always the case however as will be shown in the next example.

@@

\caption{The MC falls quickly in the first iteration before oscillating wildly on its way towards a

@@

@@

where $\|A \|_{\infty}=\max\limits_{i,j}(a_{ij})$ means the $\ell_{\infty}$-norm of a matrix $A$. We subtract the identity matrix to avoid the influence of diagonal elements, because according to the mutual coherence definition we are interested in angle between the different columns $i\neq j$. \\

@@

In order to solve this problem we used the algorithm proposed in [refer ball].
\includegraphics[width=3.4in]{initial_fp.eps}
\caption{Initial.}
\label{Fig:initial_rand}

\begin{figure}[!h]
\centering
\includegraphics[width=3.4in]{opt_fp.eps}
\caption{Difference.}
\label{Fig:diff_rand}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=3.4in]{diff_fp.eps}
\caption{Difference.}
\label{Fig:diff_rand}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=3.4in]{mc_fp_nr.eps}
\caption{Difference.}
\label{Fig:diff_rand}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=3.4in]{initial_fp_nr.eps}
\caption{Initial.}
\label{Fig:initial_rand}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=3.4in]{opt_fp_nr.eps}
\caption{Difference.}
\label{Fig:diff_rand}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=3.4in]{diff_fp_nr.eps}
\caption{Difference.}
\label{Fig:diff_rand}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=3.4in]{mc_fp_nr.eps}
\caption{Difference.}
\label{Fig:diff_rand}
\end{figure}

$\hdots$\\
To achieve mutual coherence minimization, a smoothed gradient descent technique is used.
First it is applied to the overall sensing matrix $M$. \\
$\hdots$\\
The lower bound for mutual coherence for any $m\times n$ matrix is given as:
\begin{equation}
\mu(M) \geq \sqrt{\frac{n - m}{m(n-1}}
\end{equation}

\section{Results}
The algorithm of Lin et al. is an efficient way to minimize the MC of dictionaries used
in compressive sensing applications. When compared to other current algorithms, it currently
outperforms the others in terms of convergence rate and minimization achieved.
\subsection{Problems with stability}
The only time the algorithm could not perform well was
when it was given poorly conditioned input. This includes cases where where the initial MC of the
dictionary is too close to 1 either because two or more vectors are nearly parallel or opposite. Under these circumstances the algorithm is unable to compute the gradient of the dictionary in a stable manner.

\subsection{Improving stability}
Restricting the dictionaries which are attempted to be optimized to those which do not 
include redundant or exactly opposite entries is an effective technique for maintaining stability 
when using the algorithm of Lin et al.
\section{Conclusion}
The field of CS is rapidly evolving at this time, and this is evidenced by the progress shown
in algorithms such as those developed by Lin et al. and others. The technique discussed in this paper 
provides a way to enhance the dictionary used in a CS application in a flexible manner. First, the 
underlying dictionary can be modified for better mutual coherence, guided by the matrix given by the 
direct mutual coherence minimization method. Secondly, if the underlying dictionary is fixed, the 
mutual coherence of the overall dictionary may be reduced through the application of a projection
matrix.

These bold new techniques afford more opportunity to researchers as they pursue sparser and sparser
representations for signals.
\section{References}
1.
